My Cool Title

### 2019-05-04 paper.tex
Added section describing audio interface

\subsection{Implementation}

@@

\subsubsection{Android App}

We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.

>>>>

@@

\subsection{Controller Implementation}

We made an Android app that implements the object detector and POMDP controller onto a mobile phone that can generate and provide guidance instructions for a user.  
This was done by combining an audio interface that can provide non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
Each of these aspects and their implementation are discussed here.

\subsubsection{Audio Interface}

The target audience of our system are PwVI and we therefore have to provide guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to the ambient sounds (something PwVI typically rely upon extensively), we use a set of non-intrusive bone-conducting headsets to transmit the audio signals to the user.

To describe the waypoints pan and tilt positions, we implemented an improved version of the interface described in~\cite{belloto2013} that exploits a uses a spatialised audio signal.
However, in this work we only spatialise the audio in the pan dimension only, since our headphones bypass the ear's pinnae that allow a person to determine the tilt angle of a sound source. 
Instead we exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively\todo{cite} and adjust the sound source's pitch as a function of the waypoint's tilt angle. 
With this interface and set of headphones, we are able to describe the location of a waypoint to a user in 2 dimensions (pan and tilt) in an intuitive an non-intrusive manner.

\subsubsection{Object Detector}

\subsubsection{POMDP Controller}
